paper_replication

### 2021-12-16 paper_replication.Rmd
Update paper_replication.Rmd

@@

## Table 2 ###
table1(~ Women + White.pct + Black.pct + Native.American.pct + Asian.pct + Hispanic.pct + Median.Income + College.Grad.pct + percentdem2008 | inanalysislabel, 
       data = countydem,
       overall = FALSE,
       extra.col = list(`P-value` = p_value_t_test),
       extra.col.pos = 3,
       footnote = 'P-values are derived by two sample t-tests.',
       caption = "County Data for States Included and Not Included in Analysis"
       )
```

>>>>

countydem$countyinanalysis <- ifelse(countydem$inanalysis == 1 & !is.na(countydem$AbortionRate2010), 1, 0) 
countydem$countyinanalysislabel <- factor(countydem$countyinanalysis, levels = c(1, 0), labels = c("In Analysis", "Not in Analysis"))

countydem$csinanalysis <- ifelse(sum(countydem$inanalysis + countydem$countyinanalysis) == 2, 1, 0)

@@

statesummarydata <- countydem %>% filter(csinanalysis != 2) %>% group_by(state) %>% summarize(Women = mean(Women, na.rm = TRUE), White.pct = mean(White.pct, na.rm = TRUE), Black.pct = mean(Black.pct, na.rm = TRUE), Native.American.pct = mean(Native.American.pct, na.rm = TRUE), Asian.pct = mean(Asian.pct, na.rm = TRUE), Hispanic.pct = mean(Hispanic.pct, na.rm = TRUE), College.Grad.pct = mean(College.Grad.pct, na.rm = TRUE), Median.Income = mean(Median.Income, na.rm = TRUE), percentdem2008 = mean(percentdem2008, na.rm = TRUE), AvgDistancetoProvider = mean(distancetoprovider, na.rm = TRUE), inanalysis = mean(inanalysis, na.rm = TRUE))

statesummarydata$inanalysislabel <- factor(statesummarydata$inanalysis, levels = c(1, 0), labels = c("In Analysis", "Not in Analysis"))

## Table 2 ###
table1(~ Women + White.pct + Black.pct + Native.American.pct + Asian.pct + Hispanic.pct + Median.Income + College.Grad.pct + percentdem2008 | inanalysislabel, 
       data = statesummarydata,
       overall = FALSE,
       extra.col = list(`P-value` = p_value_t_test),
       extra.col.pos = 3,
       footnote = 'P-values are derived by two sample t-tests.',
       caption = "County Data for States Included and Not Included in Analysis"
       )
```
